Revision 2: Responses to Reviewers Round 2

### 2018-10-03 jfs_submission/paper-pre-submission-revision-2/Responses-round2.Rmd
last couple of comments?

6.  Reference 8 was incomplete.  Please complete per the Information for Authors.

@@

@@

@@

@@

@@

>>>>

6.  Reference 8 was incomplete.  Please complete per the Information for Authors. *Done*

@@

*Thank you for this comment. You are right, the term sub-class characteristics is used by FTEs to describe markings that are shared across multiple tools. Some of these sub-class characteristics will be expressed in markings that can be removed by using the normalization methods suggested. 
However, normalization can del with more general structure, but at the same time will not address all sub-class structures. We have tried to clarify this point by introducing the following paragraph on page 6:

The implementation of the Chumbley score in Hadler and Morris (1) uses a normalization step before going into the optimization and validation step described below. Normalization is done by using a s LOWESS smooth to reduce extraneous structure in the markings, such as a drift, or spatial trends introduced during the barreling. To a degree, this normalization can also be used to address problems stemming from sub-class characteristics, i.e. markings in a pattern that are not unique to a single barrel but shared across a group of barrels introduced by specifics in the manufacturing process. *

@@

*We have changed the sentence to: This data forms the basis of a statistical analysis that allow us to quantify similarity of markings and serves as a basis for error rate calculations*

@@

*We now have changed all reported numbers regarding errors to percentages, including all figures.*

@@

*We have softened the sentence at the end of the paragraph. We also did not mean to make this sentence an absolute statement but were rather speculating ourselves. We have made the change to the manuscript to reflect that better.*

@@

*We are very sorry - we are completely in agreement. The original sentence was left in because of an unfortunate technical hiccup on our side. It is removed now.*
